Counting infinitely by Oritatami co-transcriptional folding

### 2019-07-17 paper.tex
wrote overflow example

\subsection{Example of overflow}

>>>>

\subsection{Example of overflow}
Oritatami system proceeds to further fold the counter transcript form the state shown in Fig.~\ref{fig:counter1stzag}, it overflows (Fig.~\ref{fig:overflowex1}).
If it does not overflow, the next module L will bind to above Turn Signal and turn.
However, since the carry overflows, module L's folding starts from bottom row and does not reach Turn Signal, so L forms a self standing glider shape, goes straight and extends the zig pass (Fig.~\ref{fig:overflowex2}).
Then the folding of module H begins and this H also becomes a glider shape (Fig.~\ref{fig:overflowex3}).
There is nothing above the folded module H (brick He1), but the original value is recognized as "0" and He1 catches the carry.
However, the end of folding He1 is bottom row because He1 is glider, so for He1 only, the counter determins that the folding end position is bottom row as carry=0.
In this way, the infinite counter extends the bit width after it overflows.

Subsequently, module R and F are folded, and then module L folding starts (Fig.~\ref{fig:overflowex4}).
Since module L turns by binding to Turn Signal, it is necessary to give signal for turn in order to move to zag pass from here.
Therefore, let the top of folded module F be Turn Signal.
Normally, there are folded beads above module F, so module L can not bind to F's Turn Signal.
However, only when it overflows, above F becomes blank, so L turns by being folded there (Fig.~\ref{fig:overflowex5}).
The turned module L forms a Turn Signal at the end, and folding of zag pass starts.
\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{fig/svg/CounterEx13_1.pdf}
\caption{
Reach the left end with carry.
Even if transcript of module L sticks to Turn Signal, it can not bind because the distance is long.
}
\label{fig:overflowex1}
\end{figure}

\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{fig/svg/CounterEx14_1.pdf}
\caption{
Module L forms a glider shape without binding to Turn Signal and goes straight on. 
}
\label{fig:overflowex2}
\end{figure}

\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{fig/svg/CounterEx15_1.pdf}
\caption{
Module H catches the overflowed carry but module H can not cancel the carry because it must be a self standing glider.
That is way the last bead of this module H is folded at the bottom but carry = 0. 
}
\label{fig:overflowex3}
\end{figure}

\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{fig/svg/CounterEx17_1.pdf}
\caption{
Module R and F are folded, and then folding of module L starts, but without Turn Signal, L can not turn.
Then, turn module L by making the top of module F the Turn Signal.
}
\label{fig:overflowex4}
\end{figure}

\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{fig/svg/CounterEx18_1.pdf}
\caption{
Module L turns by module F's Turn Signal and zag pass starts.
Also, the end of L takes the form of Turn Signal.
}
\label{fig:overflowex5}
\end{figure}
